Bow shocks, bow waves, and dust waves. IV. Shell shape statistics

### 2019-08-14 papers/Papers1234/sec-observational-diagnostics.tex
Version 3 of Paper III submitted
Hopefully the last version

In a series of papers \citeauthor{Kobulnicky:2018a} provide an
extensive mid-infrared-selected sample of over 700 candidate stellar
bow shock nebulae (\citealp{Kobulnicky:2016a, Kobulnicky:2017a,
  Kobulnicky:2018a}, hereafter K16, K17, and K18).  For 20 of these
sources, reliable distances and spectral classifications are provided
in Table~5 of K17 and Tables~1 and~2 of K18. In this section, we
outline how we obtain \(\tau\) and \(\eta\shell\) from the data in
these catalogs, while further aspects of the
\citeauthor{Kobulnicky:2018a} material are discussed in
\S~\ref{app:bow-shock-data}.  As this paper was being written, we
became aware of a new mass-loss study that greatly expands on the
earlier results of K18 (H.~Kobulnicky, priv.~comm.).  The new study
includes 70 bow shock sources and incorporates Gaia distances and
proper motions, together with new optical/IR spectroscopy of the
central stars.  Apart from making use of an updated spectral
classification of one source (\S~\ref{sec:anomalous-b-star}), we have
elected to concentrate on only the published K18 sample in this paper,
but will address the expanded sample in future publications.

@@

In principle, both methods are valid and their different assumptions
and dependencies on observed quantities and auxiliary parameters
provide an important cross check on one another.  However, as
explained in detail in \S~\ref{sec:grain-temp-emiss}, the \(j_\nu(U)\)
relation depends on the shape of the illuminating SED, which means
that the \citet{Draine:2007a} models require modification when applied
to grains around OB stars.  A further discrepancy arises due to an
interpolation error in K18, which resulted in values of \(j_{70}\)
being overestimated by about a factor of 2 for sources with weak
radiation fields (H.~Kobulnicky, priv.~comm.).

>>>>

In a series of papers \citeauthor{Kobulnicky:2018a} provide an
extensive mid-infrared-selected sample of over 700 candidate stellar
bow shock nebulae (\citealp{Kobulnicky:2016a, Kobulnicky:2017a,
  Kobulnicky:2018a}, hereafter K16, K17, and K18).  For 20 of these
sources, reliable distances and spectral classifications are provided
in Table~5 of K17 and Tables~1 and~2 of K18. In this section, we
outline how we obtain \(\tau\) and \(\eta\shell\) from the data in
these catalogs, while further aspects of the
\citeauthor{Kobulnicky:2018a} material are discussed in
\S~\ref{app:bow-shock-data}.  As this paper was being written, we
became aware of a new mass-loss study that greatly expands on the
earlier results of K18 \citep{Kobulnicky:2019a}.  The new study
includes 70 bow shock sources and incorporates Gaia distances and
proper motions, together with new optical/IR spectroscopy of the
central stars.  Apart from making use of an updated spectral
classification of one source (\S~\ref{sec:anomalous-b-star}), we have
elected to concentrate on only the published K18 sample in this paper,
but will address the expanded sample in future publications.

@@

In principle, both methods are valid and their different assumptions
and dependencies on observed quantities and auxiliary parameters
provide an important cross check on one another.  However, as
explained in detail in \S~\ref{sec:grain-temp-emiss}, the \(j_\nu(U)\)
relation depends on the shape of the illuminating SED, which means
that the \citet{Draine:2007a} models require modification when applied
to grains around OB stars.  A further discrepancy arises due to an
interpolation error in K18, which resulted in values of \(j_{70}\)
being overestimated by about a factor of 2 for sources with weak
radiation fields \citep[corrected in][]{Kobulnicky:2019a}.
